---
title: "COVID-19 patient cohort extraction"
output: html_notebook
---
#### Libraries and working directory

```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(matrixStats)
library(forecast)
library(imputeTS)
library(splines)
library(patchwork)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(gdata)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_knit$set(root.dir = "//<study_data_folder>")
```

```{r}
sessionInfo()
```
#### Load data
```{r}
episodes <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
labs <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
aande <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
contacts <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
deaths <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
trak_care <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
trak_adm <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
trak_disch <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
smr_code <- read.csv("<..>.csv", stringsAsFactors = FALSE,header=TRUE,sep='\t',quote="",check.names=FALSE, na.strings=c("NA", "N/A", "", " "))
```

#### Select lab tests for positive and negative admissions
```{r}
#### Merge with TRAK
trak_adm_ids <- unique(trak_adm$pid)
lab_data <- labs %>%
  select(c(pid, dataSource, collectionDate, testPositive))

trak_adm_sel <- trak_adm %>%
  select(c(pid, EpisodeNumber, AdmissionDate, AdmissionTime, AdmissionTypeCode, AdmissionStatus, AdmittingSpecialtyCode)) %>%
  mutate(AdmissionDateTime = ymd_hm(paste(AdmissionDate, AdmissionTime)))

trak_disch_sel <- trak_disch %>%
  select(c(pid, EpisodeNumber, DischargeDate, DischargeTime, DischargeSpecialtyCode, EpisodeLoSDays, EpisodeLoSHours)) %>%
  mutate(DischargeDateTime = ymd_hm(paste(DischargeDate, DischargeTime)))

trak_full <- left_join(trak_adm_sel, trak_disch_sel, by=c('pid', 'EpisodeNumber'))
trak_full <- trak_full %>%
  select(c(pid, AdmissionDate, AdmissionDateTime, AdmissionStatus, AdmissionTypeCode, DischargeDate, DischargeDateTime, EpisodeLoSDays, AdmittingSpecialtyCode, DischargeSpecialtyCode, EpisodeNumber)) %>%
  na.omit() %>%
  filter(AdmissionStatus %in% c('D', 'A')) %>%
  mutate(AdmissionDate = as.Date(AdmissionDate)) %>%
  mutate(DischargeDate = as.Date(DischargeDate))
```

```{r}
### Handle overlapping admissions
trak_sel <- trak_full %>%
  arrange(pid, AdmissionDate) %>%
  group_by(pid) %>%
  mutate(indx = c(0, cumsum(as.numeric(lead(AdmissionDate)) > 
                              cummax(as.numeric(DischargeDate)))[-n()])) %>%
  group_by(pid,indx) %>%
  summarise(AdmissionDate=min(AdmissionDate), DischargeDate=max(DischargeDate), EpisodeLoSDays=sum(EpisodeLoSDays), AdmittingSpecialtyCode=first(AdmittingSpecialtyCode),
            DischargeSpecialtyCode=last(DischargeSpecialtyCode), AdmissionDateTime=min(AdmissionDateTime), DischargeDateTime=max(DischargeDateTime), EpisodeNumber=first(EpisodeNumber), AdmissionTypeCode=first(AdmissionTypeCode)) %>%
  select(-indx)

head(trak_sel)
dim(trak_sel)
dim(trak_full)
```
```{r}
#### Validate numbers
table(trak_sel$AdmittingSpecialtyCode)
dim(trak_sel[trak_sel$EpisodeLoSDays==0,])

### Set elective/non-elective flag
trak_sel <- trak_sel %>%
  mutate(elective=ifelse(AdmissionTypeCode %in% c('EL', 'OP', 'R', 'WL'),1,0)) %>%
  mutate(elective=ifelse(AdmissionTypeCode %in% c('NB', 'X'), -1, elective))

### Check admission specialties
table(trak_sel$elective)
table(trak_sel$AdmittingSpecialtyCode)
table(trak_sel[trak_sel$elective==0,]$AdmittingSpecialtyCode)
```

```{r}
#### Use emergency admissions only
trak_sel <- trak_sel %>%
  filter(elective==0)
dim(trak_sel)
```

```{r}
### Merge with covid tests
lab_data <- left_join(lab_data, trak_sel, by=c('pid'))
lab_data <- lab_data[!is.na(lab_data$collectionDate),]
```


```{r}
#### Filter positive tests
lab_data$testPositive[is.na(lab_data$testPositive)] <- 'N'
### Build positive intervals
admissionInterval14 <- interval(lab_data$AdmissionDateTime - days(14), lab_data$DischargeDateTime)
admissionInterval12 <- interval(lab_data$AdmissionDateTime - days(12), lab_data$DischargeDateTime)
admissionInterval10 <- interval(lab_data$AdmissionDateTime - days(10), lab_data$DischargeDateTime)
admissionInterval8 <- interval(lab_data$AdmissionDateTime - days(8), lab_data$DischargeDateTime)
admissionInterval6 <- interval(lab_data$AdmissionDateTime - days(6), lab_data$DischargeDateTime)
lab_data$collectionDate <- ymd_hms(lab_data$collectionDate)

lab_data <- lab_data %>%
  mutate(testPositive_14d = case_when((collectionDate %within% admissionInterval14) & (testPositive == 'Y') ~1, TRUE ~0)) %>%
  mutate(testPositive_12d = case_when((collectionDate %within% admissionInterval12) & (testPositive == 'Y') ~1, TRUE ~0)) %>%
  mutate(testPositive_10d = case_when((collectionDate %within% admissionInterval10) & (testPositive == 'Y') ~1, TRUE ~0)) %>%
  mutate(testPositive_8d = case_when((collectionDate %within% admissionInterval8) & (testPositive == 'Y') ~1, TRUE ~0)) %>%
  mutate(testPositive_6d = case_when((collectionDate %within% admissionInterval6) & (testPositive == 'Y') ~1, TRUE ~0))
```

```{r}
### Filter 10d lab tests
lab_sel <- lab_data %>%
  filter(!((dataSource == 'Test by Lighthouse Laboratory') & (testPositive_10d == 0))) %>%
  select(c(pid, dataSource, collectionDate, testPositive_10d, EpisodeNumber, AdmissionDate, AdmittingSpecialtyCode, AdmissionDateTime, DischargeDate, DischargeSpecialtyCode, DischargeDateTime, EpisodeLoSDays)) %>%
  arrange(pid, AdmissionDateTime, desc(testPositive_10d)) %>%
  group_by(pid) %>%
  slice(1) %>%
  ungroup()
```

```{r}
table(lab_sel$testPositive_10d)
```


```{r}
#### Aggregate trak care data
trak_care_sel <- trak_care %>% drop_na(c(dateCreated, timeCreated))
trak_care_sel$datetime <- ymd_hm(paste(trak_care_sel$dateCreated, trak_care_sel$timeCreated))

trak_care_sel <- trak_care_sel %>%
  select(-pid) %>%
  rename_with(~paste0('tc_', .x)) %>%
  mutate(pid=trak_care_sel$pid) %>%
  relocate(pid) %>%
  select(-c('tc_dateCreated', 'tc_timeCreated'))

### Build flags for OT, PT input
trak_care_sel %>% group_by(tc_careProvider) %>% summarise(n=n()) %>% arrange(desc(n))

trak_care_sel <- trak_care_sel %>%
  select(pid)

trak_agg <- arrange(aggregate(EpisodeLoSDays ~ pid, data=lab_data, FUN=median, na.rm=TRUE), pid)
trak_agg_total <- aggregate(EpisodeLoSDays ~ pid, data=lab_data, FUN=sum, na.rm=TRUE)
trak_agg_total <- trak_agg_total %>%
  rename(Total_EpisodeLoSDays = EpisodeLoSDays)

trak_agg <- trak_agg %>%
  rename(Median_EpisodeLoSDays = EpisodeLoSDays)

### Get last discharge date and attach
trak_ddate <- trak_disch %>%
  group_by(pid) %>%
  slice(which.max(as.Date(DischargeDate, '%Y-%m-%d'))) %>%
  select(c(pid, DischargeDate))

### Get discharge specialties
lab_disch_spec <- lab_sel %>%
  mutate(spec_general_medicine=ifelse(DischargeSpecialtyCode %in% c('GM', 'GMWNT'), 1, 0)) %>%
  mutate(spec_respiratory_medicine=ifelse(DischargeSpecialtyCode %in% c('RESP', 'RESPCSNT', 'RESPFGEBNT', 'RESPPXARNT', 'RESPWANT'), 1, 0)) %>%
  mutate(spec_geriatric_medicine=ifelse(DischargeSpecialtyCode %in% c('GA', 'GORU', 'RESPITE'), 1, 0)) %>%
  select(c(pid, EpisodeNumber, spec_general_medicine, spec_respiratory_medicine, spec_geriatric_medicine)) %>%
  arrange(pid, EpisodeNumber, desc(spec_general_medicine), desc(spec_respiratory_medicine), desc(spec_geriatric_medicine)) %>%
  group_by(pid) %>%
  slice(1)

trak_agg_full <- left_join(trak_agg, trak_ddate, by='pid')
trak_agg_full <- left_join(trak_agg_full, trak_agg_total, by='pid')

trak_agg_full <- trak_agg_full %>%
  mutate(across(c(Total_EpisodeLoSDays, Median_EpisodeLoSDays), round, 3)) %>%
  rename(LastDischargeDate = DischargeDate)

### Join with pt set
lab_sel <- left_join(lab_sel, trak_agg_full, by='pid')
lab_sel <- left_join(lab_sel, lab_disch_spec, by=c('pid', 'EpisodeNumber'))
lab_sel$spec_geriatric_medicine <- lab_sel$spec_geriatric_medicine %>% replace_na(0)
lab_sel$spec_general_medicine <- lab_sel$spec_general_medicine %>% replace_na(0)
lab_sel$spec_respiratory_medicine <- lab_sel$spec_respiratory_medicine %>% replace_na(0)
lab_sel <- lab_sel[!is.na(lab_sel$EpisodeNumber),]

head(lab_sel)
```

```{r}
#### Merge with SPINE set of pts
trak_pt_ids <- unique(lab_sel$pid)
ep_cols <- c('pid', 'sex', 'simd2020Vigintile', 'simd2020Quintile', 'healthBoard', 
             'ageAtFirstTest', 'dateOfFirstTest', 'wasFirstTestPositive',
             'dateOfFirstPositiveTest', 'numberOfTests', 'numberOfPositiveTests',
             'anyPositiveTest')

ep_sel <- episodes %>% 
  select(ep_cols) %>%
  filter((ageAtFirstTest >= 18) & (pid %in% trak_pt_ids)) %>%
  select(-anyPositiveTest)

lab_full <- left_join(ep_sel, lab_sel, by='pid')
head(lab_full)
dim(lab_full)
```

#### Append Death data
```{r}
death_sel <- deaths %>%
  select(c('pid', 'Date of Death')) %>%
  rename_with(~ tolower(gsub(' ', '_', .x, fixed=TRUE)))

lab_full <- left_join(lab_full, death_sel, 'pid')
### Died during stay flag
lab_full <- lab_full %>%
  mutate(died_during_stay = ifelse(as.Date(LastDischargeDate, '%Y-%m-%d') >= 
                                     as.Date(date_of_death, '%Y-%m-%d'), 1, 0)) %>%
  mutate(died_during_stay = ifelse(is.na(died_during_stay), 0, died_during_stay)) %>%
  filter(died_during_stay == 0)

head(lab_full)
dim(lab_full)
```

#### Build flags for comorbidities
```{r}
smr_code$EventDate <- as.Date(smr_code$EventDate[!is.na(smr_code$EventDate)])
smr_code <- left_join(smr_code, lab_full[, c('pid', 'AdmissionDate')], by='pid')

smr_sel <- smr_code %>%
  filter(!is.na(AdmissionDate)) %>%
  filter(EventDate < AdmissionDate) %>%
  select(c(pid, PhenotypeName))

smr_sel$PhenotypeName <- gsub(",", "", as.character(smr_sel$PhenotypeName))

smr_cms <- within(smr_sel, {PhenotypeName <- as.character(PhenotypeName);
       Comorbidities <- ave(PhenotypeName, pid, FUN=toString)})

smr_cms <- smr_cms %>%
  select(c(pid, Comorbidities)) %>%
  group_by(pid) %>%
  slice(1)

lab_full <- left_join(lab_full, smr_cms, by='pid')

lab_full <- lab_full %>%
  mutate(n_morbid=str_split(Comorbidities, ',') %>% lengths) %>%
  mutate(n_morbid=ifelse(is.na(Comorbidities), 0, n_morbid)) %>%
  mutate(is_multimorbid=ifelse(n_morbid > 1, 1, 0)) %>%
  mutate(is_complex_multimorbid=ifelse(n_morbid > 3, 1, 0)) %>%
  mutate(cm_chd = ifelse(grepl('Coronary heart disease not otherwise specified', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_stable_angina = ifelse(grepl('Stable angina', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_unstable_angina = ifelse(grepl('Unstable Angina', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_heart_failure = ifelse(grepl('Heart failure', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_ic_haem = ifelse(grepl('Intracerebral haemorrhage', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_ischaemic_stroke = ifelse(grepl('Ischaemic stroke', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_stroke_nos = ifelse(grepl('Stroke NOS', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_mi = ifelse(grepl('Myocardial infarction', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_diabetes = ifelse(grepl('Diabetes', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_obesity = ifelse(grepl('Obesity', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_esrd = ifelse(grepl('End stage renal disease', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_urinary_incontinence = ifelse(grepl('Urinary Incontinence', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_hip_fracture = ifelse(grepl('Fracture of hip', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_osteoporosis = ifelse(grepl('Osteoporosis', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_parkinsons = ifelse(grepl('Parkinson\'s disease', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_dementia = ifelse(grepl('Dementia', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_delirium = ifelse(grepl('Delirium not induced by alcohol and other psychoactive substances', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_depression = ifelse(grepl('Depression', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_asthma = ifelse(grepl('Asthma', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_copd = ifelse(grepl('Chronic Obstructive Pulmonary Disease (COPD)', Comorbidities, fixed=TRUE), 1, 0)) %>%
  mutate(cm_stroke_any = ifelse((cm_stroke_nos==0) & (cm_ischaemic_stroke==0), 0, 1))
```

```{r}
for (phenotype in colnames(lab_full %>% dplyr::select(starts_with('cm_'))))
{
  print('------')
  print(phenotype)
  print(table(lab_full[phenotype]))
}
```
#### Build 6-month post-discharge outcomes for some of the more prevalent comorbidities
```{r}
smr_pd <- left_join(smr_code, lab_full[, c('pid', 'LastDischargeDate')], by='pid')

smr_pd$EventDate <- ymd(smr_pd$EventDate)
smr_pd$LastDischargeDate <- ymd(smr_pd$LastDischargeDate)
cm_interval <- interval(smr_pd$LastDischargeDate, smr_pd$LastDischargeDate + months(6))

smr_sel <- smr_pd %>%
  mutate(outcome_6m = case_when(EventDate %within% cm_interval ~1,
                                          TRUE ~0)) %>%
  filter(outcome_6m == 1) %>%
  select(c(pid, PhenotypeName))

smr_sel$PhenotypeName <- gsub(",", "", as.character(smr_sel$PhenotypeName))

smr_cms <- within(smr_sel, {PhenotypeName <- as.character(PhenotypeName);
       cm_6m_outcomes <- ave(PhenotypeName, pid, FUN=toString)})

smr_cms <- smr_cms %>%
  select(c(pid, cm_6m_outcomes)) %>%
  group_by(pid) %>%
  slice(1)

lab_full <- left_join(lab_full, smr_cms, by='pid')

lab_full <- lab_full %>%
  mutate(cm_chd_6m = ifelse(grepl('Coronary heart disease not otherwise specified', cm_6m_outcomes, fixed=TRUE), 1, 0)) %>%
  mutate(cm_ischaemic_stroke_6m = ifelse(grepl('Ischaemic stroke', cm_6m_outcomes, fixed=TRUE), 1, 0)) %>%
  mutate(cm_diabetes_6m = ifelse(grepl('Diabetes', cm_6m_outcomes, fixed=TRUE), 1, 0)) %>%
  mutate(cm_dementia_6m = ifelse(grepl('Dementia', cm_6m_outcomes, fixed=TRUE), 1, 0)) %>%
  mutate(cm_delirium_6m = ifelse(grepl('Delirium not induced by alcohol and other psychoactive substances', cm_6m_outcomes, fixed=TRUE), 1, 0)) %>%
  mutate(cm_copd_6m = ifelse(grepl('Chronic Obstructive Pulmonary Disease (COPD)', cm_6m_outcomes, fixed=TRUE), 1, 0))

```
```{r}
for (phenotype in colnames(lab_full %>% dplyr::select(starts_with('cm_') & ends_with('6m'))))
{
  print('------')
  print(phenotype)
  print(table(lab_full[phenotype]))
}
```


#### Build 1yr mortality after index admission
```{r}
lab_full$AdmissionDateTime <- lab_full$AdmissionDateTime[!is.na(lab_full$AdmissionDateTime)]
lab_full$DischargeDateTime <- lab_full$DischargeDateTime[!is.na(lab_full$DischargeDateTime)]
lab_full$AdmissionDate <- as.Date(lab_full$AdmissionDate[!is.na(lab_full$AdmissionDate)])
lab_full$DischargeDate <- as.Date(lab_full$DischargeDate[!is.na(lab_full$DischargeDate)])

mortality_interval <- interval(lab_full$AdmissionDate, lab_full$AdmissionDate + days(365))
lab_full$date_of_death <- as.Date(ymd(lab_full$date_of_death))

lab_full <- lab_full %>%
  mutate(mortality_1yr=case_when(date_of_death %within% mortality_interval ~1,
                                          TRUE ~0))

```
```{r}
length(lab_full$date_of_death)
length(mortality_interval)
table(lab_full$mortality_1yr)
```
```{r}
sum(is.na(trak_care$specialty))
sum(is.na(trak_care$careProvider))
```

#### Validate contacts data

```{r}
interventions <- c('Interventions - Dietetics', 'Interventions - Occupational Therapy',
                   'Interventions - Physiotherapy', 'Interventions - Speech and Language Therapy')

lab_ids <- unique(lab_full$pid)
trak_pw_test <- trak_care %>%
  filter(pid %in% lab_ids) %>%
  mutate(pt_input=ifelse(str_detect(careProvider, 'Physiotherap'), 1, 0)) %>%
  mutate(ot_input=ifelse(str_detect(careProvider, 'Occupational'), 1, 0)) %>%
  mutate(slt_input=ifelse(str_detect(careProvider, 'Speech and Language'), 1, 0)) %>%
  mutate(diet_input=ifelse(str_detect(careProvider, 'Diet'), 1, 0)) %>%
  filter((pt_input == 1) | (ot_input == 1) | (slt_input == 1) | (diet_input == 1)) %>%
  mutate(cdt = ymd(dateCreated)) %>%
  mutate(type = 'Inpatient') %>%
  mutate(intervention=case_when(pt_input == 1 ~ 'Physiotherapy', ot_input==1~'Occupational Therapy',
                                    slt_input == 1 ~ 'Speech and Language Therapy', diet_input == 1~'Dietetics', TRUE~'Undefined')) %>%
  select(c(pid, cdt, type)) %>%
  distinct()

trak_ahp_test <- contacts %>%
  filter(pid %in% lab_ids) %>%
  mutate(cdt = ymd(ContactDate)) %>%
  mutate(EpisodeSubType = ifelse((EpisodeSubType == 'Daycase'), 'Inpatient', EpisodeSubType)) %>%
  mutate(EpisodeSubType = ifelse((EpisodeSubType == 'Daycase'), 'Community', EpisodeSubType)) %>%
  filter(EpisodeSubType %in% c('Community', 'Inpatient')) %>%
  filter(InterventionCategory1 %in% interventions) %>%
  mutate(InterventionCategory1 = str_trim(sub(".*Interventions - ", "", InterventionCategory1))) %>%
  rename(type = EpisodeSubType) %>%
  rename(intervention = InterventionCategory1) %>%
  select(c(pid, cdt, type)) %>%
  distinct()

dim(trak_pw_test)
dim(trak_ahp_test)
dim(union(trak_pw_test, trak_ahp_test))
dim(intersect(trak_pw_test, trak_ahp_test))
table(union(trak_pw_test, trak_ahp_test)$type)
table(intersect(trak_pw_test, trak_ahp_test)$type)
```

```{r}
#### Merge the tables
pw_inter <- intersect(trak_pw_test, trak_ahp_test)
pw_inter <- pw_inter %>%
  drop_na() %>%
  mutate(pr_key = paste(pid, '-', cdt, '-', type))

trak_pw_test <- trak_pw_test %>%
  drop_na() %>%
  mutate(pr_key = paste(pid, '-', cdt, '-', type))

trak_ahp_test <- trak_ahp_test %>%
  drop_na() %>%
  mutate(pr_key = paste(pid, '-', cdt, '-', type))

trak_pw_all <- union(trak_pw_test, trak_ahp_test)
ahp_ids <- unique(trak_ahp_test$pr_key)
trakpw_ids <- unique(trak_pw_test$pr_key)
inter_ids <- unique(pw_inter$pr_key)
```

```{r}
### Get basic rehab data
trak_pw_all <- trak_pw_all %>%
  mutate(source = case_when((pr_key %in% inter_ids) ~ 'BOTH', (pr_key %in% trakpw_ids) ~ 'PW_TRAK',
         (pr_key %in% ahp_ids) ~ 'PW_AHP', TRUE~'Undefined'))

trak_ahp <- contacts %>%
  filter(pid %in% lab_ids) %>%
  mutate(cdt = ymd(ContactDate)) %>%
  mutate(cduration_ahp = ContactDuration) %>%
  mutate(EpisodeSubType = ifelse((EpisodeSubType == 'Daycase'), 'Inpatient', EpisodeSubType)) %>%
  mutate(EpisodeSubType = ifelse((EpisodeSubType == 'Daycase'), 'Community', EpisodeSubType)) %>%
  filter(EpisodeSubType %in% c('Community', 'Inpatient')) %>%
  filter(InterventionCategory1 %in% interventions) %>%
  mutate(InterventionCategory1 = str_trim(sub(".*Interventions - ", "", InterventionCategory1))) %>%
  rename(type = EpisodeSubType) %>%
  rename(cintervention_ahp = InterventionCategory1) %>%
  rename(ctime_ahp = ContactTime) %>%
  select(c(pid, cdt, type, ctime_ahp, cduration_ahp, cintervention_ahp, ContactMode, Intervention1, MainReasonActivity, AHPProfession, PatientLocationCategory)) %>%
  rename(contact_mode=ContactMode) %>%
  rename(intervention_details=Intervention1) %>%
  rename(activity=MainReasonActivity) %>%
  rename(specialist=AHPProfession) %>%
  rename(location_type=PatientLocationCategory) %>%
  drop_na() %>%
  mutate(pr_key = paste(pid, '-', cdt, '-', type)) %>%
  distinct(pr_key, .keep_all = TRUE)

trak_pw <- trak_care %>%
  filter(pid %in% lab_ids) %>%
  mutate(pt_input=ifelse(str_detect(careProvider, 'Physiotherap'), 1, 0)) %>%
  mutate(ot_input=ifelse(str_detect(careProvider, 'Occupational'), 1, 0)) %>%
  mutate(slt_input=ifelse(str_detect(careProvider, 'Speech and Language'), 1, 0)) %>%
  mutate(diet_input=ifelse(str_detect(careProvider, 'Diet'), 1, 0)) %>%
  filter((pt_input == 1) | (ot_input == 1) | (slt_input == 1) | (diet_input == 1)) %>%
  mutate(cdt = ymd(dateCreated)) %>%
  mutate(type = 'Inpatient') %>%
  mutate(cintervention_pw=case_when(pt_input == 1 ~ 'Physiotherapy', ot_input==1~'Occupational Therapy',
                                    slt_input == 1 ~ 'Speech and Language Therapy', diet_input == 1~'Dietetics', TRUE~'Undefined')) %>%
  
  mutate(ctime_pw = timeCreated) %>%
  mutate(activity_pw = case_when(cintervention_pw=='Physiotherapy'~'Physiotherapy interventions', 
                              cintervention_pw=='Occupational Therapy'~'Occupational therapy intervention',
                              cintervention_pw=='Speech and Language Therapy'~'Speech and Language Therapy intervention',
                              cintervention_pw=='Dietetics'~'Dietetic intervention', TRUE~'Undefined intervention')) %>%
  mutate(specialist_pw = case_when(cintervention_pw=='Physiotherapy'~'Physiotherapists', 
                              cintervention_pw=='Occupational Therapy'~'Occupational Therapists',
                              cintervention_pw=='Speech and Language Therapy'~'Speech and Language Therapists',
                              cintervention_pw=='Dietetics'~'Dieticians', TRUE~'Other')) %>%
  mutate(contact_mode_pw = 'Face to Face') %>%
  mutate(intervention_details_pw = 'No information') %>%
  mutate(location_type_pw = 'Wards / OPDs') %>%
  select(c(pid, cdt, type, ctime_pw, cintervention_pw, intervention_details_pw, activity_pw, contact_mode_pw,
           specialist_pw, location_type_pw)) %>%
  drop_na() %>%
  mutate(cduration_pw = NA) %>%
  mutate(pr_key = paste(pid, '-', cdt, '-', type)) %>%
  distinct(pr_key, .keep_all = TRUE)

trak_pw_all <- left_join(trak_pw_all, trak_ahp, by=c('pid', 'cdt', 'type', 'pr_key'))
trak_pw_all <- left_join(trak_pw_all, trak_pw, by=c('pid', 'cdt', 'type', 'pr_key'))
```

```{r}
trak_pw_all <- trak_pw_all %>%
  mutate(ctime_ahp = ifelse(is.na(ctime_ahp), '23:59', ctime_ahp)) %>%
  mutate(ctime_pw = ifelse(is.na(ctime_pw), '23:59', ctime_pw)) %>%
  rowwise() %>%
  mutate(ctime = min(ctime_ahp,ctime_pw)) %>%
  mutate(cintervention = case_when((ctime_pw < ctime_ahp)&(!is.na(cintervention_pw)) ~ cintervention_pw,
                                   (ctime_ahp < ctime_pw)&(!is.na(cintervention_ahp)) ~ cintervention_ahp,
                                   (is.na(cintervention_ahp))&(!is.na(cintervention_pw)) ~ cintervention_pw,
                                   (is.na(cintervention_pw))&(!is.na(cintervention_ahp)) ~ cintervention_ahp)) %>%
  ungroup() %>%
  mutate(cintervention = ifelse((is.na(cintervention))&(!is.na(cintervention_ahp)), cintervention_ahp, cintervention)) %>%
  mutate(cintervention = ifelse((is.na(cintervention))&(!is.na(cintervention_pw)), cintervention_pw, cintervention)) %>%
  filter(!is.na(cintervention)) %>%
  mutate(cduration = cduration_ahp) %>%
  mutate(intervention_details = ifelse(is.na(intervention_details), 'No information', intervention_details)) %>%
  mutate(contact_mode = ifelse(is.na(contact_mode), 'Face to Face', contact_mode)) %>%
  mutate(activity = ifelse(is.na(activity), case_when(cintervention=='Physiotherapy'~'Physiotherapy interventions',cintervention=='Occupational Therapy'~'Occupational therapy intervention',cintervention=='Speech and Language Therapy'~'Speech and Language Therapy intervention',cintervention=='Dietetics'~'Dietetic intervention', TRUE~'Undefined intervention'), activity)) %>%
  mutate(specialist = case_when(cintervention=='Physiotherapy'~'Physiotherapists', 
                              cintervention=='Occupational Therapy'~'Occupational Therapists',
                              cintervention=='Speech and Language Therapy'~'Speech and Language Therapists',
                              cintervention=='Dietetics'~'Dieticians', TRUE~'Other')) %>%
  mutate(location_type = ifelse(is.na(location_type), 'Wards / OPDs', location_type)) %>%
  select(c(pid, cdt, type, source, ctime, cduration, cintervention, activity, contact_mode, intervention_details, activity, specialist, location_type)) %>%
  mutate(cdtt = ymd_hm(paste(cdt, ctime)))
```
```{r}
table(trak_pw_all$cintervention)
table(trak_pw_all$source)
dim(trak_pw_all)
sapply(trak_pw_all, function(y) sum(length(which(is.na(y)))))
```

```{r}
ggplot(trak_pw_all[is.na(trak_pw_all$cduration),], aes(x=cdt, y=..density..)) + geom_histogram(bins=100)
```
```{r}
#### Impute missing durations
trak_pw_all <- trak_pw_all %>%
  arrange(pid, cdt)
trak_pw_imp_km <- na_kalman(trak_pw_all$cduration, model='StructTS')
ggplot_na_imputations(trak_pw_all$cduration, trak_pw_imp_km)
trak_pw_all$cduration_kalman <- round(trak_pw_imp_km)

trak_pw_imp_m <- na_mean(trak_pw_all$cduration)
ggplot_na_imputations(trak_pw_all$cduration, trak_pw_imp_m)
trak_pw_all$cduration_mean <- round(trak_pw_imp_m)

trak_pw_imp_ma <- na_ma(trak_pw_all$cduration, weighting='exponential')
ggplot_na_imputations(trak_pw_all$cduration, trak_pw_imp_ma)
trak_pw_all$cduration_mea <- round(trak_pw_imp_ma)

trak_pw_imp_md <- na_mean(trak_pw_all$cduration, option='median')
trak_pw_all$cduration_median <- round(trak_pw_imp_md)
trak_pw_imp_locf <- na_locf(trak_pw_all$cduration)
trak_pw_all$cduration_locf <- round(trak_pw_imp_locf)
trak_pw_imp_inter <- na_interpolation(trak_pw_all$cduration)
trak_pw_all$cduration_inter <- round(trak_pw_imp_inter)
```
```{r}
statsNA(trak_pw_all$cduration)
```

```{r}
#### Original
p <- ggplot(data=trak_pw_all, aes(x=cdt, y=cduration)) + geom_point()

p <- p + geom_smooth(aes(y=cduration), method='lm', formula=y~ns(x), se=FALSE)
p
ggplot(trak_pw_all, aes(x=cduration)) + geom_histogram(bins=100)

#### Kalman
p_s <- ggplot(data=trak_pw_all, aes(x=cdt, y=cduration_kalman)) + geom_point()

p_s <- p_s + geom_smooth(aes(y=cduration_kalman), method='lm', formula=y~ns(x), se=FALSE)
p_s
ggplot(trak_pw_all, aes(x=cduration_kalman)) + geom_histogram(bins=100)

#### EMA
p_e <- ggplot(data=trak_pw_all, aes(x=cdt, y=cduration_mea)) + geom_point()
p_e <- p_e + geom_smooth(aes(y=cduration_mea), method='lm', formula=y~ns(x), se=FALSE)
p_e
ggplot(trak_pw_all, aes(x=cduration_mea)) + geom_histogram(bins=100)
```


```{r}
### Round-up MEA
round_up <- function(x,m) m*ceiling(x/m)
round_down <- function(x,m) m*floor(x/m)
trak_pw_all$cduration_rmeaup <- round_up(trak_pw_all$cduration_mea, 5)
trak_pw_all$cduration_rmeadown <- round_down(trak_pw_all$cduration_mea, 5)
```

```{r}
p_r <- ggdensity(trak_pw_all, x='cduration', color='gray', fill='gray', xlab='Duration (original)') + xlim(0, 100) + ylim(0, 0.2)
p_med <- ggdensity(trak_pw_all, x='cduration_median', color='violet', fill='violet', xlab='Median') + xlim(0, 100) + ylim(0, 0.3)
p_inter <- ggdensity(trak_pw_all, x='cduration_inter', color='orange', fill='orange', xlab='Interpolated') + xlim(0, 100) + ylim(0, 0.2)
p_locf <- ggdensity(trak_pw_all, x='cduration_locf', color='pink', fill='pink', xlab='LOCF') + xlim(0, 100) + ylim(0, 0.2)
p_k <- ggdensity(trak_pw_all, x='cduration_kalman', color='red', fill='red', xlab='Kalman') + xlim(0, 100) + ylim(0, 0.2)
p_m <- ggdensity(trak_pw_all, x='cduration_mean', color='green', fill='green', xlab='Mean') + xlim(0, 100) + ylim(0, 0.4)
p_ema <- ggdensity(trak_pw_all, x='cduration_mea', color='blue', fill='blue', xlab='MWEA') + xlim(0, 100) + ylim(0, 0.2)
p_rema_u <- ggdensity(trak_pw_all, x='cduration_rmeaup', color='darkolivegreen', fill='darkolivegreen', xlab='RUP:MWEA') + xlim(0, 100) + ylim(0, 0.2)
p_rema_d <- ggdensity(trak_pw_all, x='cduration_rmeadown', color='darkcyan', fill='darkcyan', xlab='RDOWN:MWEA') + xlim(0, 100) + ylim(0, 0.2)
gg <- ggarrange(p_r, p_m, p_med, p_k, p_ema, p_rema_u, p_rema_d, p_inter, p_locf, nrow=3, ncol=3, common.legend=TRUE, legend='top')
annotate_figure(gg, top=text_grob('Density distributions of total rehabilitation time using various data imputation techniques', face='bold', size=12))
ggsave('//<output_folder>/<plot_file>.png', bg='white')
```

#### Evaluate methods
```{r}
set.seed(42)
trak_pw_na <- trak_pw_all %>%
  filter(!is.na(cduration))

train_ind <- sample(seq_len(nrow(trak_pw_na)), size=floor(0.661 * nrow(trak_pw_na)))
train_gt <- trak_pw_na[-train_ind,]$cduration
trak_pw_na[-train_ind, ]$cduration <- NA
perf_df <- data.frame(matrix(ncol=3, nrow=0))

## Mean
train_imp_mean <- na_mean(trak_pw_na$cduration)
rmse_mean <- round(rmse(train_gt, train_imp_mean), 4)
mae_mean <- round(mae(train_gt, train_imp_mean), 4)
perf_df <- rbind(perf_df, c('Mean', rmse_mean, mae_mean))

## Median
train_imp_med <- na_mean(trak_pw_na$cduration, option='median')
rmse_med <- round(rmse(train_gt, train_imp_med), 4)
mae_med <- round(mae(train_gt, train_imp_med), 4)
perf_df <- rbind(perf_df, c('Median', rmse_med, mae_med))

## Random
train_imp_rand <- na_random(trak_pw_na$cduration)
rmse_rand <- round(rmse(train_gt, train_imp_rand), 4)
mae_rand <- round(mae(train_gt, train_imp_rand), 4)
perf_df <- rbind(perf_df, c('Random', rmse_rand, mae_rand))

## EWMA
train_imp_ma <- na_ma(trak_pw_na$cduration, weighting='exponential')
rmse_ma <- round(rmse(train_gt, train_imp_ma), 4)
mae_ma <- round(mae(train_gt, train_imp_ma), 4)
perf_df <- rbind(perf_df, c('Exponential WMA', rmse_ma, mae_ma))

## RDOWN:EWMA
rdma <- round_down(train_imp_ma, 5)
rmse_rdma <- round(rmse(train_gt, rdma), 4)
mae_rdma <- round(mae(train_gt, rdma), 4)
perf_df <- rbind(perf_df, c('Rounded-down Exponential WMA (base 5)', rmse_rdma, mae_rdma))

## RUP:EWMA
ruma <- round_up(train_imp_ma, 5)
rmse_ruma <- round(rmse(train_gt, ruma), 4)
mae_ruma <- round(mae(train_gt, ruma), 4)
perf_df <- rbind(perf_df, c('Rounded-up Exponential WMA (base 5)', rmse_ruma, mae_ruma))

## LOCF
train_imp_locf <- na_locf(trak_pw_na$cduration)
rmse_locf <- round(rmse(train_gt, train_imp_locf), 4)
mae_locf <- round(mae(train_gt, train_imp_locf), 4)
perf_df <- rbind(perf_df, c('LOCF', rmse_locf, mae_locf))

## Kalman smoothing
train_imp_kalman <- na_kalman(trak_pw_na$cduration, model='StructTS')
rmse_kalman <- round(rmse(train_gt, train_imp_kalman), 4)
mae_kalman <- round(mae(train_gt, train_imp_kalman), 4)
perf_df <- rbind(perf_df, c('Kalman smoothing', rmse_kalman, mae_kalman))

## Linear interpolation
train_imp_inter <- na_interpolation(trak_pw_na$cduration)
rmse_inter <- round(rmse(train_gt, train_imp_inter), 4)
mae_inter <- round(mae(train_gt, train_imp_inter), 4)
perf_df <- rbind(perf_df, c('Linear interpolation', rmse_inter, mae_inter))

colnames(perf_df) <- c('Method', 'RMSE', 'MAE')
perf_df
```
```{r}
#### Export best results
write.csv(trak_pw_all, "//<output_folder>/<imputed_contacts_file>.csv", row.names=FALSE)
```

#### Generate contact features

```{r}
trak_pw_all <- read.csv("//<output_folder>/<imputed_contacts_file>.csv")
```

```{r}
### Merge trak contacts
lab_contacts <- left_join(lab_full[, c('pid', 'AdmissionDate', 'DischargeDate')], trak_pw_all, by=c('pid'))
lab_contacts$AdmissionDate <- lubridate::ymd(lab_contacts$AdmissionDate)
lab_contacts$DischargeDate <- lubridate::ymd(lab_contacts$DischargeDate)
lab_contacts$cdt <- lubridate::ymd(lab_contacts$cdt)
lab_contacts <- lab_contacts %>%
  filter((AdmissionDate < cdt) & (DischargeDate >= cdt)) %>%
  # Out-of-hours contacts are set after 7PM and before 7AM
  mutate(out_of_hours = ifelse((hm(as.character(ctime)) > hm('19:00')) | (hm(as.character(ctime)) < hm('07:00')), 1, 0)) %>%
  filter(type=='Inpatient')

table(lab_contacts$type)
```

```{r}
### Create trak pathway rehab features
interv_sel <- lab_contacts %>%
  arrange(pid, cdt) %>%
  mutate(time_to_therapy = as.numeric(difftime(cdt, AdmissionDate, units=c('days'))))

first_interv <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, time_to_therapy)) %>%
  group_by(pid) %>%
  slice(1)

second_interv <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, time_to_therapy)) %>%
  group_by(pid) %>%
  rename(time_to_therapy_2=time_to_therapy) %>%
  slice(2)

first_type <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, type)) %>%
  group_by(pid) %>%
  slice(1)

second_type <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, type)) %>%
  group_by(pid) %>%
  rename(type_2=type) %>%
  slice(2)

first_interv_name <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, cintervention)) %>%
  group_by(pid) %>%
  slice(1)

second_interv_name <- interv_sel %>%
  arrange(pid, AdmissionDate) %>%
  select(c(pid, cintervention)) %>%
  group_by(pid) %>%
  rename(cintervention_2=cintervention) %>%
  slice(2)

n_contact_count <- interv_sel %>%
  select(pid) %>%
  group_by(pid) %>%
  summarise(total_count_rehab = n())

n_ooh_contact_count <- interv_sel %>%
  filter(out_of_hours==1) %>%
  select(pid) %>%
  group_by(pid) %>%
  summarise(total_count_ooh_rehab = n())

n_contact_minutes <- interv_sel %>%
  select(c(pid, cduration_rmeadown)) %>%
  group_by(pid) %>%
  summarise(total_mins_rehab = sum(cduration_rmeadown))

n_ooh_contact_minutes <- interv_sel %>%
  filter(out_of_hours==1) %>%
  select(c(pid, cduration_rmeadown)) %>%
  group_by(pid) %>%
  summarise(total_sum_ooh_rehab = sum(cduration_rmeadown))

### List of intervention types
interv_types <- within(interv_sel, {cintervention <- as.character(cintervention);
rehab_interventions <- ave(cintervention, pid, FUN=toString)})

interv_types <- interv_types %>%
  select(c(pid, rehab_interventions)) %>%
  group_by(pid) %>%
  slice(1)
  
lab_full <- left_join(lab_full, interv_types, by='pid')
lab_full <- left_join(lab_full, first_type, by='pid')
lab_full <- left_join(lab_full, second_type, by='pid')
lab_full <- left_join(lab_full, n_contact_count, by='pid')
lab_full <- left_join(lab_full, n_ooh_contact_count, by='pid')
lab_full <- left_join(lab_full, n_contact_minutes, by='pid')
lab_full <- left_join(lab_full, n_ooh_contact_minutes, by='pid')
lab_full <- left_join(lab_full, first_interv, by='pid')
lab_full <- left_join(lab_full, second_interv, by='pid')
lab_full <- left_join(lab_full, first_interv_name, by='pid')
lab_full <- left_join(lab_full, second_interv_name, by='pid')

lab_full$time_to_therapy[is.na(lab_full$time_to_therapy)] <- -1
lab_full$time_to_therapy_2[is.na(lab_full$time_to_therapy_2)] <- -1
lab_full$time_to_therapy <- round(lab_full$time_to_therapy)
lab_full$time_to_therapy_2 <- round(lab_full$time_to_therapy_2)
lab_full$total_count_rehab[is.na(lab_full$total_count_rehab)] <- 0
lab_full$total_count_ooh_rehab[is.na(lab_full$total_count_ooh_rehab)] <- 0
lab_full$cintervention[is.na(lab_full$cintervention)] <- 'No intervention'
lab_full$cintervention_2[is.na(lab_full$cintervention_2)] <- 'No intervention'
lab_full$total_sum_ooh_rehab[is.na(lab_full$total_sum_ooh_rehab)] <- 0
lab_full$total_mins_rehab[is.na(lab_full$total_mins_rehab)] <- 0
```


```{r}
#### Build outcome flags
lab_full$received_rehab <- ifelse(lab_full$time_to_therapy > -1, 1, 0)
table(lab_full[lab_full$received_rehab==1,]$type)
table(lab_full[lab_full$received_rehab==1,]$testPositive_10d)
table(lab_full$received_rehab)

lab_full <- lab_full %>%
  rowwise() %>%
  mutate(ttt_diff = time_to_therapy_2 - time_to_therapy) %>%
  mutate(same_interv = ifelse((cintervention == cintervention_2) & (cintervention != 'No intervention'), 1, 0)) %>%
  ungroup() %>%
  # Get 7-day contact fields
  mutate(second_contact_7d = ifelse((ttt_diff <= 7) & (cintervention != 'No intervention')
                                      & (cintervention_2 != 'No intervention'), 1, 0)) %>%
  mutate(first_contact_7d = ifelse((ttt_diff > 7) & (cintervention != 'No intervention')
                                      & (cintervention_2 != 'No intervention'), 1, 0)) %>%
  mutate(no_contacts_7d = ifelse((cintervention == 'No intervention')
                                      & (cintervention_2 == 'No intervention'), 1, 0)) %>%
  mutate(second_contact_7d = case_when(second_contact_7d==1~'2+', first_contact_7d==1~'1', 
                                       no_contacts_7d==1~'0', TRUE~'0'))

table(lab_full$second_contact_7d)
prop.table(table(lab_full$second_contact_7d))
prop.table(table(lab_full[lab_full$second_contact_7d=='2+',]$testPositive_10d))
table(lab_full[lab_full$second_contact_7d=='2+',]$testPositive_10d)


table(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==0),]$cintervention_2)
table(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$cintervention_2)

sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$total_count_rehab)
```
```{r}
lab_full <- lab_full %>%
  mutate(n_physio = str_count(lab_full$rehab_interventions, "Physiotherapy")) %>%
  mutate(n_physio = ifelse(is.na(n_physio), 0, n_physio)) %>%
  mutate(n_occ = str_count(lab_full$rehab_interventions, "Occupational Therapy")) %>%
  mutate(n_occ = ifelse(is.na(n_occ), 0, n_occ)) %>%
  mutate(n_diet = str_count(lab_full$rehab_interventions, "Dietetics")) %>%
  mutate(n_diet = ifelse(is.na(n_diet), 0, n_diet)) %>%
  mutate(n_spl = str_count(lab_full$rehab_interventions, "Speech and Language Therapy")) %>%
  mutate(n_spl = ifelse(is.na(n_spl), 0, n_spl))

sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==0),]$n_physio)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==0),]$n_occ)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==0),]$n_diet)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==0),]$n_spl)

sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$n_physio)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$n_occ)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$n_diet)
sum(lab_full[(lab_full$second_contact_7d=='2+')&(lab_full$testPositive_10d==1),]$n_spl)
```

```{r}
table(lab_full$testPositive_10d)
```



#### Deal with missing data
```{r}
lab_full$simd2020Vigintile[is.na(lab_full[,'simd2020Vigintile'])] <- as.numeric(round(mean(lab_full$simd2020Vigintile, na.rm=TRUE)))
lab_full$simd2020Quintile[is.na(lab_full[,'simd2020Quintile'])] <- as.numeric(round(mean(lab_full$simd2020Quintile, na.rm=TRUE)))

dim(lab_full)
table(lab_full$simd2020Quintile)
table(lab_full$simd2020Vigintile)
sapply(lab_full, function(y) sum(length(which(is.na(y)))))
```
```{r}
### LOS fix
lab_full <- lab_full %>%
  mutate(index_LOS = round(as.numeric(difftime(DischargeDateTime, AdmissionDateTime, units='days')), 2))
```


#### Export
```{r}
#### Export results
write.csv(lab_full, "//<output_folder>/<cohort_file>.csv", row.names=FALSE)
```